---
title: "CodeBook"
author: "Naveen Srikanth"
date: "Sunday, September 21, 2014"
output: html_document
---
#Smart phone activity data description
- Volunteers=30
- Activities Performed by public who used smart phone=WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING
- The dataset has been partitioned in to two parts training data of 70% and testing aData of 30%

#Variables

##merged data: the data table containing the merged training and test dataset from X_test.txt and X_train.txt. This amounts to 10299 observations with 564 columns. The columns include the 561 features stated in features.txt and added Subject, Activity Id, and Activity columns which are taken from the various activities.txt and y labels. Column headers are included.

##Reading the data
```{r}
testData <- read.table("C:/Users/NAVEEN SRIKANTHD/Downloads/Dataset/UCI HAR Dataset/test/X_test.txt",header=FALSE)
Test_Act <- read.table("C:/Users/NAVEEN SRIKANTHD/Downloads/Dataset/UCI HAR Dataset/test/y_test.txt",header=FALSE)
Test_Sub <- read.table("C:/Users/NAVEEN SRIKANTHD/Downloads/Dataset/UCI HAR Dataset/test/subject_test.txt",header=FALSE)
trainData <- read.table("C:/Users/NAVEEN SRIKANTHD/Downloads/Dataset/UCI HAR Dataset/train/X_train.txt",header=FALSE)
Train_Act <- read.table("C:/Users/NAVEEN SRIKANTHD/Downloads/Dataset/UCI HAR Dataset/train/y_train.txt",header=FALSE)
Train_Sub <- read.table("C:/Users/NAVEEN SRIKANTHD/Downloads/Dataset/UCI HAR Dataset/train/subject_train.txt",header=FALSE)

activities <- read.table("C:/Users/NAVEEN SRIKANTHD/Downloads/Dataset/UCI HAR Dataset/activity_labels.txt",header=FALSE,colClasses="character")
Test_Act$V1 <- factor(Test_Act$V1,levels=activities$V1,labels=activities$V2)
Train_Act$V1 <- factor(Train_Act$V1,levels=activities$V1,labels=activities$V2)

```


##Uses descriptive activity names to name the activities in the data set
```{r}
features <- read.table("C:/Users/NAVEEN SRIKANTHD/Downloads/Dataset/UCI HAR Dataset/features.txt",header=FALSE,colClasses="character")
colnames(testData)<-features$V2
colnames(trainData)<-features$V2
colnames(Test_Act)<-c("Activity")
colnames(Train_Act)<-c("Activity")
colnames(Test_Sub)<-c("Subject")
colnames(Train_Sub)<-c("Subject")
head(features)
```
##Merging the data
```{r}
testData<-cbind(testData,Test_Act)
testData<-cbind(testData,Test_Sub)
trainData<-cbind(trainData,Train_Act)
trainData<-cbind(trainData,Train_Sub)
DataSet<-rbind(testData,trainData)
#Number of rows
nrow(DataSet)
#Number of columns
ncol(DataSet)
#Head
head(DataSet)
```

##Extract only the measurements on the mean and standard deviation for each measurement.
```{r}
#DataSet_mean<-apply(DataSet,FUN=mean,MARGIN=1,na.omit=TRUE)
#DataSet_sd<-sapply(DataSet,sd,na.rm=TRUE)
```

##Setting the data in proper format
```{r}
DT <- data.frame(DataSet)
#Number of rows
nrow(DT)
#Number of columns
ncol(DT)
#Head of Dataset
head(DT)
```

##Below code describes about the independent tidy data set with the average of each variable for each activity and each subject.
```{r}
#tidy<-DT[,lapply(.SD,mean),by="Activity,Subject"]
```

##Below code gives the consolidated dataset 
```{r}
#write.table(tidy,file="E:/tidy.txt",sep=",",row.names = FALSE)
```